---
title: "County-Dashboard"
execute:
  warning: false
  message: false
---


<h2 style="font-size: 2rem;">Minnesota Counties</h2>

<div class="county-grid">

<a href="#aitkin" class="county-button">Aitkin</a>
<a href="#anoka" class="county-button">Anoka</a>
<a href="#becker" class="county-button">Becker</a>
<a href="#beltrami" class="county-button">Beltrami</a>
<a href="#benton" class="county-button">Benton</a>
<a href="#bigstone" class="county-button">Big Stone</a>
<a href="#carlton" class="county-button">Carlton</a>
<a href="#carver" class="county-button">Carver</a>
<a href="#chippewa" class="county-button">Chippewa</a>
<a href="#chisago" class="county-button">Chisago</a>
<a href="#clay" class="county-button">Clay</a>
<a href="#clearwater" class="county-button">Clearwater</a>
<a href="#cook" class="county-button">Cook</a>
<a href="#crow-wing" class="county-button">Crow Wing</a>
<a href="#douglas" class="county-button">Douglas</a>
<a href="#hennepin" class="county-button">Hennepin</a>
<a href="#hubbard" class="county-button">Hubbard</a>
<a href="#isanti" class="county-button">Isanti</a>
<a href="#itasca" class="county-button">Itasca</a>
<a href="#lyon" class="county-button">Lyon</a>
<a href="#millelacs" class="county-button">Mille Lacs</a>
<a href="#olmsted" class="county-button">Olmsted</a>
<a href="#otter-tail" class="county-button">Otter Tail</a>
<a href="#ramsey" class="county-button">Ramsey</a>

</div>

---

<details id="aitkin">
<summary><strong>Aitkin County</strong></summary>

```{r}
#| echo: FALSE
library(sf)
library(leaflet)
library(htmltools)
data <- readRDS("Data/aitkin_parcels_sf.rds")

labels <- lapply(data$OWNER_NAME, HTML)

leaflet(data) |>
  addTiles() |>
  addPolygons(
    label = labels
  )
```

</details>

<details id="anoka">
<summary><strong>Anoka County</strong></summary>

```{r}
#| echo: FALSE
library(sf)
library(leaflet)
library(htmltools)
data <- readRDS("Data/anoka_parcels_sf.rds")

labels <- lapply(data$OWNER_NAME, HTML)

leaflet(data) |>
  addTiles() |>
  addPolygons(
    label = labels
  )
```

</details>

<details id="becker">
<summary><strong>Becker County</strong></summary>

```{r}
#| echo: FALSE
library(sf)
library(leaflet)
library(htmltools)
data <- readRDS("Data/becker_parcels_sf.rds")

labels <- lapply(data$OWNER_NAME, HTML)

leaflet(data) |>
  addTiles() |>
  addPolygons(
    label = labels
  )
```

</details>

<details id="beltrami">
<summary><strong>Beltrami County</strong></summary>

```{r}
#| echo: FALSE
library(sf)
library(leaflet)
library(htmltools)
data <- readRDS("Data/beltrami_parcels_sf.rds")

labels <- lapply(data$OWNER_NAME, HTML)

leaflet(data) |>
  addTiles() |>
  addPolygons(
    label = labels
  )
```

</details>

<details id="benton">
<summary><strong>Benton County</strong></summary>

```{r}
#| echo: FALSE
library(sf)
library(leaflet)
library(htmltools)
data <- readRDS("Data/benton_parcels_sf.rds")

labels <- lapply(data$OWNER_NAME, HTML)

leaflet(data) |>
  addTiles() |>
  addPolygons(
    label = labels
  )
```


<details id="bigstone">
<summary><strong>Big Stone County</strong></summary>

```{r}
#| echo: FALSE
library(sf)
library(leaflet)
library(htmltools)
data <- readRDS("Data/aitkin_parcels_sf.rds")

labels <- lapply(data$OWNER_NAME, HTML)

leaflet(data) |>
  addTiles() |>
  addPolygons(
    label = labels
  )
```

</details>

<details id="carlton">
<summary><strong>Carlton County</strong></summary>

```{r}
#| echo: FALSE
library(sf)
library(leaflet)
library(htmltools)
data <- readRDS("Data/carlton_parcels_sf.rds")

labels <- lapply(data$OWNER_NAME, HTML)

leaflet(data) |>
  addTiles() |>
  addPolygons(
    label = labels
  )
```

</details>

<details id="carver">
<summary><strong>Carver County</strong></summary>

```{r}
#| echo: FALSE
library(sf)
library(leaflet)
library(htmltools)
data <- readRDS("Data/carver_parcels_sf.rds")

labels <- lapply(data$OWNER_NAME, HTML)

leaflet(data) |>
  addTiles() |>
  addPolygons(
    label = labels
  )
```

</details>

<details id="chippewa">
<summary><strong>Chippewa County</strong></summary>

```{r}
#| echo: FALSE
library(sf)
library(leaflet)
library(htmltools)
data <- readRDS("Data/chippewa_parcels_sf.rds")

labels <- lapply(data$OWNER_NAME, HTML)

leaflet(data) |>
  addTiles() |>
  addPolygons(
    label = labels
  )
```

</details>

<details id="chisago">
<summary><strong>Chisago County</strong></summary>

```{r}
#| echo: FALSE
library(sf)
library(leaflet)
library(htmltools)
data <- readRDS("Data/chisago_parcels_sf.rds")

labels <- lapply(data$OWNER_NAME, HTML)

leaflet(data) |>
  addTiles() |>
  addPolygons(
    label = labels
  )
```

</details>

<details id="clay">
<summary><strong>Clay County</strong></summary>

```{r}
#| echo: FALSE
library(sf)
library(leaflet)
library(htmltools)
data <- readRDS("Data/clay_parcels_sf.rds")

labels <- lapply(data$OWNER_NAME, HTML)

leaflet(data) |>
  addTiles() |>
  addPolygons(
    label = labels
  )
```

</details>

<details id="clearwater">
<summary><strong>Clearwater County</strong></summary>

```{r}
#| echo: FALSE
library(sf)
library(leaflet)
library(htmltools)
data <- readRDS("Data/clearwater_parcels_sf.rds")

labels <- lapply(data$OWNER_NAME, HTML)

leaflet(data) |>
  addTiles() |>
  addPolygons(
    label = labels
  )
```

</details>

<details id="cook">
<summary><strong>Cook County</strong></summary>

```{r}
#| echo: FALSE
library(sf)
library(leaflet)
library(htmltools)
data <- readRDS("Data/cook_parcels_sf.rds")

labels <- lapply(data$OWNER_NAME, HTML)

leaflet(data) |>
  addTiles() |>
  addPolygons(
    label = labels
  )
```

</details>

<details id="crow-wing">
<summary><strong>Crow Wing County</strong></summary>

```{r}
#| echo: FALSE
library(sf)
library(leaflet)
library(htmltools)
data <- readRDS("Data/crowwing_parcels_sf.rds")

labels <- lapply(data$OWNER_NAME, HTML)

leaflet(data) |>
  addTiles() |>
  addPolygons(
    label = labels
  )
```


<details id="douglas">
<summary><strong>Douglas County</strong></summary>

```{r}
#| echo: FALSE
library(sf)
library(leaflet)
library(htmltools)
data <- readRDS("Data/douglas_parcels_sf.rds")

labels <- lapply(data$OWNER_NAME, HTML)

leaflet(data) |>
  addTiles() |>
  addPolygons(
    label = labels
  )
```


<details id="hennepin">
<summary><strong>Hennepin County</strong></summary>

```{r}
#| echo: FALSE
library(sf)
library(leaflet)
library(htmltools)
data <- readRDS("Data/hennepin_parcels_sf.rds")

labels <- lapply(data$OWNER_NAME, HTML)

leaflet(data) |>
  addTiles() |>
  addPolygons(
    label = labels
  )
```

</details>

<details id="hubbard">
<summary><strong>Hubbard County</strong></summary>

```{r}
#| echo: FALSE
library(sf)
library(leaflet)
library(htmltools)
data <- readRDS("Data/hubbard_parcels_sf.rds")

labels <- lapply(data$OWNER_NAME, HTML)

leaflet(data) |>
  addTiles() |>
  addPolygons(
    label = labels
  )
```


<details id="itasca">
<summary><strong>Itasca County</strong></summary>

```{r}
#| echo: FALSE
library(sf)
library(leaflet)
library(htmltools)
data <- readRDS("Data/itasca_parcels_sf.rds")

labels <- lapply(data$OWNER_NAME, HTML)

leaflet(data) |>
  addTiles() |>
  addPolygons(
    label = labels
  )
```

</details>

<details id="lyon">
<summary><strong>Lyon County</strong></summary>

```{r}
#| echo: FALSE
library(sf)
library(leaflet)
library(htmltools)
data <- readRDS("Data/lyon_parcels_sf.rds")

labels <- lapply(data$OWNER_NAME, HTML)

leaflet(data) |>
  addTiles() |>
  addPolygons(
    label = labels
  )
```

</details>

<details id="millelacs">
<summary><strong>Mille Lacs County</strong></summary>

```{r}
#| echo: FALSE
library(sf)
library(leaflet)
library(htmltools)
data <- readRDS("Data/millelacs_parcels_sf.rds")

labels <- lapply(data$OWNER_NAME, HTML)

leaflet(data) |>
  addTiles() |>
  addPolygons(
    label = labels
  )
```


<details id="olmsted">
<summary><strong>Olmsted County</strong></summary>

```{r}
#| echo: FALSE
library(sf)
library(leaflet)
library(htmltools)
data <- readRDS("Data/olmsted_parcels_sf.rds")

labels <- lapply(data$OWNER_NAME, HTML)

leaflet(data) |>
  addTiles() |>
  addPolygons(
    label = labels
  )
```

</details>

<details id="otter-tail">
<summary><strong>Otter Tail County</strong></summary>

```{r}
#| echo: FALSE
library(sf)
library(leaflet)
library(htmltools)
data <- readRDS("Data/ottertail_parcels_sf.rds")

labels <- lapply(data$OWNER_NAME, HTML)

leaflet(data) |>
  addTiles() |>
  addPolygons(
    label = labels
  )
```

<details id="ramsey">
<summary><strong>Ramsey County</strong></summary>

```{r}
#| echo: FALSE
library(sf)
library(leaflet)
library(htmltools)
data <- readRDS("Data/ramsey_parcels_sf.rds")

labels <- lapply(data$OWNER_NAME, HTML)

leaflet(data) |>
  addTiles() |>
  addPolygons(
    label = labels
  )
```

</details>